#cant deal with
#no Title here!
\bibitem{anpr} J.D. Barrow and K. Yamamoto. Phys. Rev. D \textbf{82}, 063516
(2010) J.D. Barrow and C. Ganguly, Class. Quantum Grav. \textbf{33},125004
(2016)
\end{thebibliography}

#no title here!->but can find link to title:D
\bibitem{Gisin3}
N. Walenta, A. Burg, D. Caselunghe, J. Constantin, N. Gisin, O. Guinnard, R. Houlmann, P. Junod, B. Korzh, N. Kulesza, M. Legr\'e,
C.C.W. Lim, T. Lunghi, L. Monat, C. Portmann, M. Soucarros, P. Trinkler, G. Trolliet, F. Vannel, and H. Zbinden,
{\href{https://dx.doi.org/10.1088/1367-2630/16/1/013047}{New J. Phys. {\bf 16} 013047 (2014)}}.

#cant deal with it yet->can be easily appended to work!
\bibitem [{\citenamefont {Cohen-Tannoudji}\ \emph {et~al.}(1992)\citenamefont
  {Cohen-Tannoudji}, \citenamefont {Dupont-Roc}, \citenamefont {Grynberg},\
  and\ \citenamefont {Thickstun}}]{cohenbook92a}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
  {Cohen-Tannoudji}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
  {Dupont-Roc}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
  {Grynberg}}, \ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
  {Thickstun}},\ }\href@noop {} {\emph {\bibinfo {title} {Atom-photon
  interactions: basic processes and applications}}}\ (\bibinfo  {publisher}
  {Wiley Online Library},\ \bibinfo {year} {1992})\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Lehmberg}(1970{\natexlab{a}})}]{lehmberg70a}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~H.}\ \bibnamefont
  {Lehmberg}},\ }\href {\doibase 10.1103/PhysRevA.2.883} {\bibfield  {journal}
  {\bibinfo  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume} {2}},\
  \bibinfo {pages} {883} (\bibinfo {year} {1970}{\natexlab{a}})}\BibitemShut
  {NoStop}%

#cant deal with it!
\bibitem{shalm2015strong}
L.~K. Shalm, E.~Meyer-Scott, B.~G. Christensen, P.~Bierhorst, M.~A. Wayne,
  M.~J. Stevens, T.~Gerrits, S.~Glancy, D.~R. Hamel, M.~S. Allman, K.~J.
  Coakley, S.~D. Dyer, C.~Hodge, A.~E. Lita, V.~B. Verma, C.~Lambrocco,
  E.~Tortorici, A.~L. Migdall, Y.~Zhang, D.~R. Kumor, W.~H. Farr, F.~Marsili,
  M.~D. Shaw, J.~A. Stern, C.~Abell\'an, W.~Amaya, V.~Pruneri, T.~Jennewein,
  M.~W. Mitchell, P.~G. Kwiat, J.~C. Bienfang, R.~P. Mirin, E.~Knill, and S.~W.
  Nam, \enquote{Strong loophole-free test of local realism,} Phys. Rev. Lett.
  \textbf{115}, 250402 (2015).

#can deal with it but needs to additionally parse unidentified field
\bibitem{hermenegildo11:ciao-design-tplp-shorter}
Hermenegildo, M., Bueno, F., Carro, M., L\'{o}pez, P., Mera, E., Morales, J.,
  Puebla, G.:
\newblock {A}n {O}verview of {C}iao and its {D}esign {P}hilosophy.
\newblock TPLP \textbf{12}(1--2) (2012)  219--252


#Can deal with but cleanup necessary
#cleanup of enclosing \newblock{} necessary
\bibitem{DIT}
F.~Dress, H.~Iwaniec, and G.~Tenenbaum.
\newblock {Sur une somme liee a la fonction de Mobius}.
\newblock {\em J. Reine Angew. Math.}, 340:53--58, 1983.

#cleanup of \enquote{
\bibitem{shalm2015strong}
L.~K. Shalm, E.~Meyer-Scott, B.~G. Christensen, P.~Bierhorst, M.~A. Wayne,
  M.~J. Stevens, T.~Gerrits, S.~Glancy, D.~R. Hamel, M.~S. Allman, K.~J.
  Coakley, S.~D. Dyer, C.~Hodge, A.~E. Lita, V.~B. Verma, C.~Lambrocco,
  E.~Tortorici, A.~L. Migdall, Y.~Zhang, D.~R. Kumor, W.~H. Farr, F.~Marsili,
  M.~D. Shaw, J.~A. Stern, C.~Abell\'an, W.~Amaya, V.~Pruneri, T.~Jennewein,
  M.~W. Mitchell, P.~G. Kwiat, J.~C. Bienfang, R.~P. Mirin, E.~Knill, and S.~W.
  Nam, \enquote{Strong loophole-free test of local realism,} Phys. Rev. Lett.
  \textbf{115}, 250402 (2015).

#Can deal with
\bibitem{Hestenes.2002}
D.~Hestenes, \emph{New Foundations for Classical Mechanics}, 2nd~ed., ser.
  Fundamental theories of physics.\hskip 1em plus 0.5em minus 0.4em\relax
  Dordrecht: {Springer Netherlands}, 2002, vol.~99.

\bibitem{Dorst.2009}
L.~Dorst, D.~Fontijne, and S.~Manning, \emph{Geometric algebra for computer
  science: An object-oriented approach to geometry}, 2nd~ed., ser. The Morgan
  Kaufmann series in computer graphics.\hskip 1em plus 0.5em minus 0.4em\relax
  Amsterdam [u.a.]: {Morgan Kaufmann/Elsevier}, 2009.
